Appendix S1: Supporting Tables and Figures

### 2022-01-18 ms/SI.Rmd
Update SI
Move description of grain-size selection to main MS
Update MS

**`r s_figure("grain-size")`**. Effect of grain size on sampling redundancy. (a), Percent of grid cells with redundancy > 0.5 by grain size (side length of square grid cells set to 10 km, 20 km, 30 km, or 40 km). (b), Percent of grid cells with redundancy = 0 by grain size. (c), Distribution of redundancy values by grain size. There is a sudden improvement in redundancy values from 10 km to 20 km, but less improvement as grain size is increased beyond 20 km.

@@

**`r s_figure("abundance")`**. Observed number of specimens (a) and sampling redundancy (b) per 0.2° grid cell in the ferns of Japan.

@@

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(values = canape_cols) +
  annotation_scale(location = "tl", width_hint = 0.2) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

a <- plot_genus("a", "Equisetum")
b <- plot_genus("b", "Deparia")
c <- plot_genus("c", "Cyrtomium")
d <- plot_genus("d", "Dryopteris")
e <- plot_genus("e", "Pteris")
f <- plot_genus("f", "Diplazium") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm"))

>>>>

**`r s_figure("grain-size")`**. Effect of grain size on sampling redundancy. (a), Percent of grid cells with redundancy > 0.5 by grain size (side length of square grid cells set to 10 km, 20 km, 30 km, or 40 km). (b), Percent of grid cells with redundancy = 0 by grain size. (c), Distribution of redundancy values by grain size.

@@

**`r s_figure("abundance")`**. Observed number of specimens (a) and sampling redundancy (b) per 20 km grid cell in the ferns of Japan.

@@

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(
    values = canape_cols,
    na.value = "transparent") +
  annotation_scale(location = "tl", width_hint = 0.2) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

a <- plot_genus("A", "Equisetum")
b <- plot_genus("B", "Deparia")
c <- plot_genus("C", "Cyrtomium")
d <- plot_genus("D", "Dryopteris")
e <- plot_genus("E", "Pteris")
f <- plot_genus("F", "Diplazium") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm"))
